Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-24 conclusions.tex
Edits to introduction (also adding section labels to some other files).
Tweaked conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

In this paper, we have presented the algorithms underlying \enzo, an
open-source adaptive mesh refinement code designed for
self-gravitating compressible fluid dynamics, including the effects of
magnetic fields, radiation transport, and a variety of microphysical
and subgrid processes.  In addition, we have described the \enzo\ code
development process, have shown the outputs of some representative
test problems, and have provided information about \enzo's performance
and parallel scaling on recent supercomputing platforms.  The \enzo\
code, its test suite, and all of the scripts used to generate plots
and figures for this paper are open source and are available at the
\enzo\ website, http://enzo-project.org.  Furthermore, the yt toolkit,
which is designed to analyze \enzo\ data (as well as data from a wide
variety of other simulation tools), can be found at its website,
http://yt-project.org.  Both of these codes have active user and
developer communities, extensive documentation and user suppport, and
strong mechanisms for users to contribute their changes and fixes to
the codebase.

@@

\begin{itemize}
\item The creation of a hybrid-parallel version of \enzo, combining
MPI for communication between nodes of a supercomputer and OpenMP for
thread-based parallelism within a node.  This will reduce on-node
memory usage and overall scaling behavior.
\item The restructuring of \enzo's treatment of particles to
accommodate a wider range of ``active'' particles that can easily
interact with each other and with multiple grids, and include sink,
source, and particle creating, splitting, and merging functionality.
\item A new HYPRE-based AMR gravity solver that is faster, more
accurate, and more scalable than the current multigrid solver.
\item New infrastructure for problem initialization, enabling
  users to more quickly and easily create new types of simulations.
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec.conclusions}

In this paper, we have presented the algorithms underlying \enzo, an
open-source adaptive mesh refinement code designed for
self-gravitating compressible fluid dynamics, including the effects of
magnetic fields, radiation transport, and a variety of microphysical
and subgrid processes.  In addition, we have described the \enzo\ code
development process, have shown the outputs of a set of representative
test problems, and have provided information about \enzo's performance
and parallel scaling on recent supercomputing platforms.  The \enzo\
code, its test suite, and all of the scripts used to generate plots
and figures for this paper are open source and are available at the
\enzo\ website, \url{http://enzo-project.org}.  Furthermore, the yt toolkit,
which is designed to analyze \enzo\ data (as well as data from a wide
variety of other simulation tools), can be found at its website,
\url{http://yt-project.org}.  Both of these codes have active user and
developer communities, extensive documentation and user suppport, and
strong mechanisms for users to contribute their changes and fixes to
the codebase.

@@

\begin{itemize}
\item The creation of a hybrid-parallel version of \enzo, combining
MPI for communication between nodes of a supercomputer and OpenMP for
thread-based parallelism within a node.  This will reduce on-node
memory usage and overall scaling behavior.
\item The restructuring of \enzo's treatment of particles to
accommodate a wider range of ``active'' particles that can easily
interact with each other and with multiple grids, and include sink,
source, and particle creation, destruction, splitting, and merging functionality.
\item A new HYPRE-based AMR gravity solver that is faster, more
accurate, and more scalable than the current multigrid solver.
\item New infrastructure for problem initialization, enabling
  users to more quickly and easily create new types of simulations.
\end{itemize}
